\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 cfhtlens.tex
text for Fig 2

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIS}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.  As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBI statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/IntegKsip.pdf}\\
\includegraphics[width=0.5\textwidth]{figures/IntegCOSEBIs.pdf}\\
\includegraphics[width=0.5\textwidth]{figures/IntegMap.pdf}
\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ and $M_{\rm ap}$.
All the values are normalized with respect to their maximum value. Two cases are shown for each statistic. 
For COSEBIs this is an angular range indicated in the caption. For aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
}
\end{center}
\end{figure}

>>>>

\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.  Figure~\ref{fig:filters} shows the integrands of these statistics for two cases,
normalised to their maximum value.
The top plot shows the integrand of $\xi_+$ for $\theta=100'$ and $\theta=350'$. 
Note that the bottom left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
angular separation of $100'$. However, in \citet{kilbinger/etal:2013} which is the same data used in \citet{kitching/etal:2016} 
the maximum $\theta$ is $350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges,
$[1',100']$ and $[0.8',350']$ which corresponds to the largest angular range used in \citet{kilbinger/etal:2013}. Here we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
Finally, the bottom panel shows the integrands of aperture mass dispersion statistics, for two maximum angular ranges, discussed above. 
As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.   
If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.  This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.  This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/IntegKsip.pdf}\\
\includegraphics[width=0.5\textwidth]{figures/IntegCOSEBIs.pdf}\\
\includegraphics[width=0.5\textwidth]{figures/IntegMap.pdf}
\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
All the values are normalized with respect to their maximum value. Two cases are shown for each statistic. 
For COSEBIs this is an angular range indicated in the caption. For aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence here we only show the lowest mode $E_1$. 
}
\end{center}
\end{figure}
